Do investors in clean energy ETFs herd?

### 2024-10-10 alt_energy_herding.qmd
fixed table footers

```{r setup}
#| include=FALSE
options(scipen=999)
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 500, 
                      fig.pos = "H", 
                      fig.env= 'figure', 
                      tab.topcaption = TRUE,
                      ft.align = "left",
                      ft.arraystretch = 0.5
                      )
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(officedown)
library(modelsummary)
library(sandwich)
library(lmtest)

@@

```{r}
#| label: tbl-herding
#| tbl-cap: "Estimation results of herding in the U.S. equity alternative energy ETFs"
#| cache: false
#| ft.arraystretch: 0.9

@@

tribble(
  ~ "gamma_0", ~ "gamma_1", ~ "gamma_2",
  "0.0038**", "0.2883***", " -1.2773***",
  "(47.09)", "(33.333)", "(-9.71)"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, part = "header", value = as_paragraph(as_equation(estimates))) %>% 
  autofit(add_w = 0.8)

@@

tribble(
  ~ "Quantile", ~ "gamma_0", ~ "gamma_1", ~ "gamma_2",
  "10%", "0.0016***", "0.2536***", " -1.3736",
  "25%", "0.0026***", "0.2461***", " -1.1056***",
  "50%", "0.0037***", "0.2648***", " -1.165***",
  "75%", "0.0048***", "0.3011***", " -1.1473***",
  "90%", "0.0064***", "0.2999***", " 0.2314"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, j = c(2, 3, 4), part = "header", value = as_paragraph(as_equation(headings))) %>% 
  mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
  add_footer_lines(values = as_paragraph(
    "This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (2) in various quantiles 10, 25, 50, 75 and 90% of the returns distribution. *,**,*** denotes significance at 10%,5% and 1% respectively."
  )) %>% 
  autofit(add_w = 0.2)

@@

tribble(
  ~ "Quantile", ~ "gamma_0", ~ "gamma_1", ~ "gamma_2", ~ "gamma_3", ~ "gamma_4",
  "10%", "0.0016***", "0.2532***", " -1.3669***", " -0.2522***", " -1.1522",
  "25%", "0.0026***", "0.2475***", " -1.2383**", " -0.2477***", " -1.1171***",
  "50%", "0.0038***", "0.2247***", " 0.3838", " -0.2634***", " -1.3144***",
  "75%", "0.0050***", "0.2500***", " 1.3135", " -0.2785***", " -0.9721***",
  "90%", "0.0065***", "0.2788***", " 1.0169", " -0.2942***", " -1.2003***"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, j = c(2, 3, 4, 5, 6), part = "header", value = as_paragraph(as_equation(headings))) %>% 
  mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
  add_footer_lines(
    values = as_paragraph(
     "This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (3). *,**,***denotes significance at 10%,5% and 1% respectively."
    )
  ) %>%
  autofit(add_w = -0.2)

@@

```{r}
#| label: fig-rolling_window
#| fig.cap: "Rolling window herding estimates"
#| cache: false
#| fig.width: 8
#| fig.height: 6

@@

tribble(
  ~ "Variable", ~ "Coefficient",
  "Transition Risk", "-4.607***",
  "Physical Risk", "-1.318", 
  "Constant", " -1.506***",
  "LogL", "-484.7",
  "Observations with Dependent Variable (Dep) = 0", "1816",
  "Observations with Dependent Variable (Dep) = 1", "134"
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1, part = "all") %>%
  add_footer_lines(
    values = as_paragraph(
      "Notes: **,*** denotes statistically significant at 5% and 1%"
    )
  ) %>% 
  autofit(add_w = 1.5)

@@

tribble(
  ~" ", ~ "High", ~ "Low",
  "Physical Risk", "-6.736*", "-6.118",
  "Transition Risk", "-1.798", "-2.581",
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1, part = "all") %>%
  add_footer_lines(
    values = as_paragraph(
      "Notes: *, denotes statistically significant at 10%"
    )
  ) %>%
  autofit(add_w = 1.4)

>>>>

```{r setup}
#| include=FALSE
options(scipen=999)
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 500, 
                      fig.pos = "H", 
                      fig.env= 'figure', 
                      tab.topcaption = TRUE,
                      ft.align = "left",
                      ft.arraystretch = 0.7
                      )
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(officedown)
library(modelsummary)
library(sandwich)
library(lmtest)

@@

```{r}
#| label: tbl-herding
#| tbl-cap: "Estimation results of herding in the U.S. equity alternative energy ETFs"
#| cache: true
#| ft.arraystretch: 0.9

@@

tribble(
  ~ "gamma_0", ~ "gamma_1", ~ "gamma_2",
  "0.0038**", "0.2883***", " -1.2773***",
  "(47.09)", "(33.333)", "(-9.71)"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, part = "header", value = as_paragraph(as_equation(estimates))) %>% 
    add_footer_lines(values = as_paragraph(
    "Note: *,**,*** denotes significance at 10%,5% and 1% respectively."
  )) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  autofit(add_w = 0.8)

@@

tribble(
  ~ "Quantile", ~ "gamma_0", ~ "gamma_1", ~ "gamma_2",
  "10%", "0.0016***", "0.2536***", " -1.3736",
  "25%", "0.0026***", "0.2461***", " -1.1056***",
  "50%", "0.0037***", "0.2648***", " -1.165***",
  "75%", "0.0048***", "0.3011***", " -1.1473***",
  "90%", "0.0064***", "0.2999***", " 0.2314"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, j = c(2, 3, 4), part = "header", value = as_paragraph(as_equation(headings))) %>% 
  mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
  add_footer_row(values = as_paragraph("Note: This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation 2 in various quantiles 10, 25, 50, 75 and 90% of the returns distribution.", " ", "*,**,*** denotes significance at 10%,5% and 1% respectively."
  ), colwidths = 4) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  autofit(add_w = 0.2)

@@

tribble(
  ~ "Quantile", ~ "gamma_0", ~ "gamma_1", ~ "gamma_2", ~ "gamma_3", ~ "gamma_4",
  "10%", "0.0016***", "0.2532***", " -1.3669***", " -0.2522***", " -1.1522",
  "25%", "0.0026***", "0.2475***", " -1.2383**", " -0.2477***", " -1.1171***",
  "50%", "0.0038***", "0.2247***", " 0.3838", " -0.2634***", " -1.3144***",
  "75%", "0.0050***", "0.2500***", " 1.3135", " -0.2785***", " -0.9721***",
  "90%", "0.0065***", "0.2788***", " 1.0169", " -0.2942***", " -1.2003***"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, j = c(2, 3, 4, 5, 6), part = "header", value = as_paragraph(as_equation(headings))) %>% 
  mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
  add_footer_row(
    values = as_paragraph("Note: This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (3). *,**,***denotes significance at 10%,5% and 1% respectively."
    ),
    colwidths = 6
  ) %>%
   hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  autofit(add_w = -0.2)

@@

```{r}
#| label: fig-rolling_window
#| fig.cap: "Rolling window herding estimates"
#| cache: true
#| fig.width: 8
#| fig.height: 6

@@

tribble(
  ~ "Variable", ~ "Coefficient",
  "Transition Risk", "-4.607***",
  "Physical Risk", "-1.318", 
  "Constant", " -1.506***",
  "LogL", "-484.7",
  "Observations with Dependent Variable (Dep) = 0", "1816",
  "Observations with Dependent Variable (Dep) = 1", "134"
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1, part = "all") %>%
  add_footer_lines(
    values = as_paragraph(
      "Notes: **,*** denotes statistically significant at 5% and 1%"
    )
  ) %>% 
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  autofit(add_w = 1.5)

@@

tribble(
  ~" ", ~ "High", ~ "Low",
  "Physical Risk", "-6.736*", "-6.118",
  "Transition Risk", "-1.798", "-2.581",
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1, part = "all") %>%
  add_footer_lines(
    values = as_paragraph(
      "Notes: *, denotes statistically significant at 10%"
    )
  ) %>%
  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
  autofit(add_w = 1.4)

### 2024-10-10 alt_energy_herding.tex
fixed table footers

@@

\renewcommand*{\arraystretch}{0.5}

@@

\multicolumn{4}{>{\raggedright}m{\dimexpr 5.54in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (2)\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.\ *,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\

@@

\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\

>>>>

\multicolumn{3}{>{\raggedright}m{\dimexpr 5.96in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ *,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\

@@

\renewcommand*{\arraystretch}{0.7}

@@

\multicolumn{4}{>{\raggedright}m{\dimexpr 5.54in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ 2\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{*,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\

@@

\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
